Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-14 main.tex
Update on Overleaf.

% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
\title{Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}

@@

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x. stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas. (\textit{... more...})
% Discuss common modeling assumptions in CE models that
%    can be addressed here:
%        1) instantaneous recycling approximation
%        2) No metal mass loading of winds, or uniform 
%           loading across species
%        3) Uniform metal abundances across the ISM (one zone)
%
%  To some degree, cosmological simulations with comparably
%     low spatial resolution face the same problems, where
%     variations and spreads in abundances (esp. across 
%     species) can be smoothed over due to the low res. or
%     the particular details of the feedback methods and
%     yield injection methods.

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}). % more on mixing
Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillota2018}. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

%\begin{figure}
%\centering
%\includegraphics[width=0.95\linewidth]{sfr_snrx100_agb.png}\\
%\caption{}
%\label{fig:sfr}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.99\linewidth]{species_bar.png}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals. \textbf{Need to font sizes and mass labels}}
\label{fig:species_fractions}
% GB(AE): Why are H and He different? Either discuss or remove from plot.
%  ------ AE removed from plot
%
\end{figure}

>>>>

% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
% AE: Had a hard time coming up with a succinct and interesting sounding title that
%     fit both of the interesting results: 
%          1) analytic PDF fits and 2) variations in metal mixing...
\title{Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source}

%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}

@@

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas. 
%
% get a sentence with a better punch at the end
%

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}). Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.99\linewidth]{species_bar.png}\\
\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom). The leftmost bar in each plot shows the sum of all metals.}
\label{fig:species_fractions}
\end{figure}
